```{r setup, include=FALSE}

####################
####################
##MODEL DEFINITION##
####################
####################

setwd(dirname(rstudioapi::getActiveDocumentContext()$path)) # PS Doesn't work when sourced from outside of rstudio

source("./grind.r")   
library(tidyverse)                   # libraries inclusions (installed with install.packages("name"))
library(ggplot2)
library(dplyr)
library(grid)
library(gridExtra)
library(scales)
library(ggrepel)
library(RColorBrewer)


# BELOW IS THE ODE-MODEL DEFINITION.:
model <- function(t, state, parms) {
  with(as.list(c(state,parms)), {
    
    phi <- (1+b-w*h)*Cp + (1-w*h)*Np + (1+b)*C + (1)*N
    
    dCp <- (1+b-w*h)*Cp - l*Cp + h*Np*Cp + h*Np*C - phi*Cp 
    dNp <- (1-w*h)*Np + l*Cp - h*Np*Cp - h*Np*C - phi*Np
    
    dC <- (1+b)*C - l*C - phi*C 
    dN <- (1)*N + l*C - phi*N
    
    
    
    return(list(c(dCp, dNp, dC, dN)))
  })
}  
``` 


``````{r Figure_Allee_Effect, echo=FALSE}
###########################################################
###########################################################
alldat<-data.frame()   # creates emtpy data frame
trajectory = 1
for (Dinv in seq(0.0,0.60,0.1))
{  
  for (Ainv in seq(0.0,0.60,0.1))
  {  
    
      for (bloop in c(0.0175,0.025))
      {
          for(wloop in seq(0.2,0.2,by=0.010))
          {
            for(hloop in seq(0.02,0.02,by=0.001))
            {
            b =  bloop
            w = wloop
            l = 0.02
            h=hloop
            
            crit1 = min(l/(b+h),1)
            crit2 = b*(1-l/(b+h))/h
            phistar = (1+b-w*h)*(1-l/(b+h)) + (1-w*h)*(l/(b))
            cat('.')
            p <- c(w=w,l=l,h=h,b=b)
           
            
            Aset = max(min(l/(b),1),0)
            Dset = min(max(1-l/b,0),1)
            
           
            
            s<-c(Cp=Dinv,Np=Ainv,C=Dset,N=Aset)
            f<-run(30000,tstep=10,timeplot=F,table=T)
            Dplus=f["Cp"]                            # store found C
            Aplus=f["Np"]
            attractor = 1
            if(tail(Dplus,1)>0.01) attractor = 2 
            C=f["C"]                            # store found C
            N=f["N"]   
            alldat <- rbind(alldat,data.frame(Dplus=Dplus,Aplus=Aplus,C=C,N=N,crit1=crit1,crit2=crit2,w=wloop,b=bloop,h=hloop,test="maintainable",time=f$time,Dinv=Dinv,Ainv=Ainv,trajectory=trajectory,attractor=attractor))
            trajectory = trajectory + 1
            }    
        }
      }
  }
          cat('\n')    

}

head(alldat %>% filter(b %in% c(0.04)) )


alldat2<-alldat %>% filter(b %in% c(0.018))

alldat2<-alldat 
top <- alldat2 %>% 
  ggplot(aes(x=Cp,y=Np,group=trajectory)) +
  geom_path(data=alldat2 %>% filter(time%in%c(0,1:1000,10000)), aes(col=as.factor(attractor)),lwd=1.0,alpha=0.25) +
  
  geom_point(size=3,pch=21,aes(fill=as.factor(attractor)),data=alldat2 %>% group_by(trajectory) %>% filter(time==min(time))) +
  geom_point(size=5,pch=22,aes(fill=as.factor(attractor)),data=alldat2 %>% group_by(trajectory) %>% filter(trajectory%in% c(10,11)) %>% filter(time==max(time))) +
  geom_path(data=alldat2 %>% filter(time%in%c(0,1:1000,10000)) %>% filter(trajectory%in% c(10,11,40,41)), arrow=arrow(),lwd=1.50,alpha=1.00) +
  theme_bw() +
  guides(fill=F,col=F)+
  facet_wrap(~b,nrow=1)

top

bot <-alldat2 %>% filter(trajectory %in% c(10,11)) %>%
  ggplot(aes(x=time,y=Np,group=trajectory)) +
  geom_line(col="purple",lwd=1)+
  geom_line(aes(y=Cp),col="green",lwd=1)+
  geom_line(aes(y=C),col="green",lty=2,lwd=1)+
  geom_line(aes(y=N),col="purple",lty=2,lwd=1)+
  theme_bw() +
  xlim(0,5000)+
  guides(fill=F,col=F)+
  facet_wrap(~b,nrow=1)

bot2 <-alldat2 %>% filter(trajectory %in% c(40,41)) %>%
  ggplot(aes(x=time,y=Np,group=trajectory)) +
  geom_line(col="purple",lwd=1)+
  geom_line(aes(y=Cp),col="green",lwd=1)+
  geom_line(aes(y=C),col="green",lty=2,lwd=1)+
  geom_line(aes(y=N),col="purple",lty=2,lwd=1)+
  theme_bw() +
    xlim(0,5000)+

  guides(fill=F,col=F)+
  facet_wrap(~b,nrow=1)

grid.arrange(top,bot,bot2)

```
